CF Nutrition Pre- and Post-CFTR Modulator

### 2022-09-22 Edith Zemanick/CF Nutrition/cf_nutrition.qmd
grammar mistakes and minor formatting

```{r}
#

```

@@

# Grouped by First Modulator

>>>>

```{r}
# Import - see cf_nutrition_clean_data.py
df = read.csv("/Users/timvigers/Documents/Work/Vigers/CF/Edith Zemanick/CF Nutrition/Data_Cleaned/analysis.csv")
df$Timepoint = factor(df$Timepoint,levels = c("Pre","Post"))
```

@@

# Baseline value grouped by first modulator

```{r}
t1 = tableby(First.Modulator~Vitamin.A+Vitamin.D+Vitamin.E.Alpha+
           ppFEV1+BMI.Percentile,data = df[df$Timepoint == "Pre",])
summary(t1,pfootnote = T)
```
